A generalized definition of multidimensional item response theory parameters

### 2023-01-13 output/paper_draft/paper_M2PLM_parameters.Rmd
Includes new version of the first empirical example table
Ignores messages in chunk outputs

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png"),
  fig.pos = "!H"
)

@@

```{r libraries}
#| message: false
```

```{r sources}
#| message: false
```

@@

```{r read-chunks-empirical-example}
read_chunk("src/Empirical_example.R")
```

```{r libraries, message=FALSE}
```

```{r sources, message=FALSE}
```

```{r read-items, message=FALSE}
```

```{r orthogonal-params}
```

```{r oblique-params}
```

```{r params-table}
```

```{r compose-empirical-items-table}
```

```{r set-flextable-wd, cache=FALSE}
```{r set-flextable-wd}
#| cache: false
```

>>>>

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      =   300,
  dev.args = list(type = "cairo-png"),
  fig.pos  = "!H"
)

@@

```{r libraries}
```

```{r sources}
```

@@

```{r read-chunks-empirical-example}
source("src/Empirical_example_Reckase2009.R", encoding = 'UTF-8')
```

```{r set-flextable-wd}
#| cache: false
```
